%! TEX root = ../main.tex
\newpage
\section{Design} \label{design}

%FIX: PLACEHOLDER
The design of the sample apps' audio processing will be implemened using the best practices for audio processing design [CITE].

Specifically, a circular buffer will be used to read data from the microphone, process it, and write it to the speaker. Audio will be stored using 16-bit PCM encoding. Audio will be stored using 32-bit floating point encoding. Audio will be processed in 10 millisecond chunks, with a sampling rate of 48 kilohertz. 

\subsection{Evaluation}

Two sets of criteria have been developed to evaluate and compare React Native and Flutter, and the audio that they can produce.
The framework criteria involves the infrastructure, development experience, and capabilities of each framework as seen in table \ref{tab:frameworks}.
For audio, objective criteria will be used to measure latency and STOI scores, along with subjective feedback from test subjects as seen in table \ref{tab:audio criteria}.
The frameworks will also be evaluated using some objective statistics, specifically data from the 2025 StackOverflow Developer Survey \cite{stackoverflow_technology}.
These statistics will be taken into account as part of the 'Community and Support Criteria.

\subsubsection{Framework Criteria}

\begin{table}[htbp]
	\caption{Criteria for framework evaluation}\label{tab:frameworks}
	\begin{center}
		\begin{tabular}[c]{|p{0.4\linewidth}|p{0.6\linewidth}|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Criteria}} & 
			\multicolumn{1}{|c|}{\textbf{Description}} \\
			\hline
			% FIX: reword this a bit
			\textbf{Community and Support} & Rating of the framework's `popularity' based on the amount of available third-party support, documentation, and libraries/packages available \\
			\hline
			\textbf{Features} & Features that the framework can use in apps, e.g. native UI components, device-specific hardware access, etc.\\
			\hline
			\textbf{Learning Curve} & The time and effort required for a new user to start developing apps with the framework, and the amount of framework-specific knowledge that is required to use the framework\\
			\hline
			\textbf{Environment Features} & The development tools offereed by the framework, such as graphical UI editors, live editing, device simulators, and IDE extensions\\
			
			\hline
		\end{tabular}
	\end{center}
\end{table}

The data taken from the 2025 StackOverflow Developer Survey gives some insight into the prevalence of different frameworks and the programming languages that they use, and in turn the amount of support a developer can expect to find on StackOverflow.
The question tag system on StackOverflow is also used to determine how many questions are being asked regarding each framework and its associated language.

\subsubsection{Audio Criteria}

\begin{table}[htbp]
	\caption{Criteria for audio evaluation}\label{tab:audio criteria}
	\begin{center}
		\begin{tabular}[c]{|p{0.4\linewidth}|p{0.6\linewidth}|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Criteria}} & 
			\multicolumn{1}{|c|}{\textbf{Description}} \\
			\hline
			\textbf{Latency} & When processing live audio, the delay between input and output \\
			\hline
			\textbf{Speech Intelligiblity} & When processing speech, the STOI [CITE] of output audio compared to input audio\\
			\hline
			\textbf{Subjective User Tests} & Tests will be conducted with potential users to evaluate apps' audio quality\\
			\hline
		\end{tabular}
	\end{center}
\end{table}

Audio quality will be objectively evaluated by measuring live processing latency and intelligibility.
Latency can be simply measured by sending an impulse as an input, and measuring the time it takes for that impulse to be processed and played back.
This process will be repeated multiple times and the results will be averaged. 
Non-live audio latency will be measured by measuring the time taken to process an audio file, taking into account the size of the audio file and any other settings regarding processing, e.g. sampling rate, and bit depth.
Both of these measurements can be performed in the app's code, and could be used as a feature to provide information to the user.

STOI 
